### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
add

	\textbf{The gap between the theory and experiment in Fig 2.b?} Thanks to R2 and R3 for pointing out this gap.
	We have improved our result so that the theory matches experiment in Fig 2.b (see Figure \ref{fig_update} for the updated result).
	For the new results, we use some delicate free probability techniques to obtain an exact asymptotic limit of the bias term {\color{red}(I am not sure what details you need here)}. %DESCRIBE THE IDEA.

@@

	\textbf{Response to R5.}
\end{document}

>>>>

	\textbf{The gap between the theory and experiment in Fig 2.b?} Thanks to R2 and R3 for pointing out this gap.
	We have improved our result so that the theory matches experiment in Fig 2.b (see Figure \ref{fig_update} for the updated result).
	To derive the new results, we use the identity $\tr\left[(X_1^\top X_1 + X_2^\top X_2)^{-2}(X_1^\top X_1)^2\right]= \left.\frac{\rm{d}}{{\rm d} t}\right|_{t=0} \tr\left[(X_1^\top X_1 + t(X_1^\top X_1)^2 + X_2^\top X_2)^{-1}\right]$. To calculate the trace of the inverse of $X_1^\top X_1 + t(X_1^\top X_1)^2 + X_2^\top X_2$, we need to study its asymptotic eigenvalue distribution for $t$ close to 0. This is complicated but can be done with an extension of the method in our paper.  %DESCRIBE THE IDEA.

@@

	\textbf{Response to R5.}

\end{document}
